Using Genetic Algorithms to Find Approximations for the Minimum Vertex Cover Problem

### 2018-02-20 paper.tex
done. will be looking for better formatting

{
\begin{wrapfigure}{r}{0.25\textwidth}
\hfill
\includegraphics[width=0.9\linewidth]{hiast}
\end{wrapfigure}

\setlength{\parindent}{0cm}
Syrian Arab Republic\\
Higher Institute for Applied Sciences and Technology\\
Informatics Department\\
Fourth Year\\
}

%\begin{flushleft}
\noindent Syrian Arab Republic\\
Higher Institute for Applied Sciences and Technology\\
Informatics Department \\
Fourth Year\\
%\end{flushleft}

>>>>

{
\begin{wrapfigure}{r}{0.20\textwidth}
\hfill
\includegraphics[width=0.9\linewidth]{hiast}
\end{wrapfigure}

\ \\[1.0mm]
Syrian Arab Republic\\
Higher Institute for Applied Sciences and Technology\\
Informatics Department\\
Fourth Year\\
}
